Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-12 submission/appendix.tex
typo fix

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results.
All results have been produced using the weightwatcher tool (v0.2.7).
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and huggingface~\cite{higgingface} distributions, as specified in the \texttt{requirements.txt} file.

@@

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=2.5cm]{img/imagenet1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=2.5cm]{img/cifar10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=2.5cm]{img/cifar100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=2.5cm]{img/svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=2.5cm]{img/cub200_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{\charles{Preliminary charts:} PL exponent $\alpha$ vs. reported Top1 Test Accuracies for pretrained DNNs available\charles{ref} for 5 different data sets.}

    \label{fig:DSalphas}
\end{figure}

>>>>

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results.
All results have been produced using the weightwatcher tool (v0.2.7).
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and huggingface~\cite{huggingface} distributions, as specified in the \texttt{requirements.txt} file.

@@

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=2.5cm]{img/imagenet1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=2.5cm]{img/cifar10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=2.5cm]{img/cifar100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=2.5cm]{img/svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=2.5cm]{img/cub200_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{\charles{Preliminary charts:} PL exponent $\alpha$ vs. reported Top1 Test Accuracies for pretrained DNNs available\charles{ref} for 5 different data sets.}
    \label{fig:DSalphas}
\end{figure}
